### 2021-06-04 README.Rmd
added docs folder

```{r message=FALSE,warning=FALSE,eval=TRUE,results='asis'}
tab1 <- summarise_onsets(df = CSS_Song2, 
                         instr = c('Clave','Bass','Guitar','Tres'))
print(knitr::kable(tab1,digits = 1,
     caption = 'Descriptives for the onset time differences (ms)'))
```

@@

There are several variants of this summary, but let's move on.

@@

```{r fig4,fig.width=4.5, fig.height=4.5, warning=FALSE}
inst<-c('Clave','Bass','Guitar','Tres') # Define instruments 
dn <- sync_execute_pairs(CSS_Song2,inst,N,10,'SD')
fig2 <- plot_by_pair(dn)  # plot
print(fig2)  
```

For more examples, see [vignette IN PROGRESS](http://) and associated [paper IN PROGRESS](http://).

>>>>

```{r message=FALSE,warning=FALSE,eval=TRUE,results='asis'}
tab1 <- summarise_onsets(df = CSS_Song2, 
                         instr = c('Clave','Bass','Guitar','Tres'))
print(knitr::kable(tab1,digits = 1,
     caption = 'Descriptives for the onset time differences (ms).'))
```

@@

There are several variants of this summary that create different summaries of the onsets across the beats, but let's move on.

@@

```{r fig4,warning=FALSE}
inst<-c('Clave','Bass','Guitar','Tres') # Define instruments 
dn <- sync_execute_pairs(CSS_Song2,inst,N,10,'SD')
fig2 <- plot_by_pair(dn)  # plot
print(fig2)  
```

For more examples, see [docs IN PROGRESS](https://tuomaseerola.github.io/onsetsync/) and associated [paper IN PROGRESS](http://).
